Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-16 awipev-CO2 copy.Rmd
beleated update

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
library(plotly)
library(htmlwidgets)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered, temp_durafet = HW_Temperature1_filtered, temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)

d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_hour TO d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_insitu_ctd)), by="closest_datetime")

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_ctd = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_insitu_ctd,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_ctd)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_ctd = mean(pH_s_seafet_temp_ctd, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_fb = mean(pH_s_durafet_temp_fb, na.rm = T))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(sal_fb = mean(sal_fb, na.rm = T),
                   temp_fb = mean(temp_fb, na.rm = T),
                   at_mean_interp = mean(at_mean_interp, na.rm = T),
            at = mean(at, na.rm = T),
            qflag_at = mean(qflag_at, na.rm = T),
            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
            ct = mean(ct, na.rm = T),
            qflag_ct = mean(qflag_ct, na.rm = T)
            )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019

@@

discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))

carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")

discrete_no_na$phcalc<- carb$pH
discrete_no_na$pco2calc<- carb$pCO2

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc<- NA
discrete_is_na$pco2calc<- NA
discrete <- rbind(discrete_no_na, discrete_is_na)
discrete <-discrete%>%dplyr::arrange(datetime)
```

```{r Combine discrete and continous data, echo=FALSE}

# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
# remove the drop_na() because of seafet/durafet line with na
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_ctd) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

```{r Depth filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#Make groups

d_all <- d_all%>%
  dplyr::mutate(depth = ifelse(pressure_insitu_ctd_filtered <=2, "1 m", 
                        ifelse(pressure_insitu_ctd_filtered >2 & pressure_insitu_ctd_filtered <=4, "3 m", 
                        ifelse(pressure_insitu_ctd_filtered >4 & pressure_insitu_ctd_filtered <=6, "5 m",
                        ifelse(pressure_insitu_ctd_filtered >6 & pressure_insitu_ctd_filtered <=8, "7 m",
                        ifelse(pressure_insitu_ctd_filtered >8, "9 m",NA))))))
```

```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#### filter salinities above 28
d_all <- d_all%>%
  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
 d_all <- d_all%>%
  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
                               ifelse (pressure_insitu_ctd_filtered >=8 ,sal_insitu_ctd, NA )))
### remove sal_mix datat that seem to be to high compared to sal_fb
  d_all <- d_all%>%
  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
                          ifelse(datetime > "2018-05-28 06:00:00" & datetime < "2018-06-03 13:00:00" , NA,
                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
                               ifelse (pressure_insitu_ctd_filtered >=8 ,temp_insitu_ctd, NA )))
```

@@

#SAL MIX
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)

@@

dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD)", ylab="Salinity") %>%
      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "S") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)

@@

dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "T") %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb)

@@

    dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd)

@@

dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%

@@

  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically. Salinity from FB is taken in consideration. If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m). New column "sal_mix" is created.

- 1 SBE45 inside the Ferrybox (sal_fb)
- 5 CTD > 8 meters depth (sal_insitu_ctd)

@@

### **Sal FB / Sal CTD > 8 m **

Property-property salinity plot using:

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2)

# date format into charactere
d_all$datetime_chr <- as.character(d_all$datetime)

p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_point( aes(color=factor(datetime_chr))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
   scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()

print(p_sal_fb_ctd)

d_all$diff_sal_fb_insitu <- d_all$sal_insitu_ctd - d_all$sal_fb
mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)

### Plotly
# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
# filename.html <- paste0("p_p_sal_fb_ctd.html")
# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")

@@

```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
  dyLegend(show = "onmouseover")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  dyAxis( "y2",valueRange = c(25, 36))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
Temperature in situ at 11 m depth is taken in consideration. If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m). New column "temp_mix" is created. For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD > 8 meters depth (temp_insitu_ctd)
- 1 fixed at 11 meters depth (temp_insitu_11m)

@@

### **T Ferrybox / T insitu 11 m **

Property-property temperature plot using:

fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
                temp_fb = ifelse(temp_fb >15, NA, temp_fb))

fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)

p_temp_11_fb<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(datetime_chr))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
print(p_temp_11_fb)

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
knitr::opts_chunk$set(echo = TRUE)

@@

@@

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet))
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_field = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_field = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_field = mean(pH_s_seafet_temp_field, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_field = mean(pH_s_durafet_temp_field, na.rm = T))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(sal = mean(salinity_field, na.rm = T),
            temp = mean(temp_field, na.rm = T),
            at_mean_interp = mean(at_mean_interp, na.rm = T),
            at = mean(at, na.rm = T),
            qflag_at = mean(qflag_at, na.rm = T),
            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
            ct = mean(ct, na.rm = T),
            qflag_ct = mean(qflag_ct, na.rm = T)
            )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019

@@

carb <- carb(15, discrete$at*1e-6, discrete$ct*1e-6,S=discrete$sal, T=discrete$temp, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
discrete$phcalc<- carb$pH
discrete$pco2calc<- carb$pCO2
```

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
```

```{r Combine discrete and continous data, echo=FALSE}
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
# remove the drop_na() because of seafet/durafet line with na
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

@@

#SAL
sal_xts <- dplyr::select(d_all, datetime, sal)%>%
  dplyr::filter(sal >28)

@@

dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
      dySeries("sal", color = "blue", strokeWidth = 0, label = "S") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)

@@

dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
      dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)

@@

    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)

@@

dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%

@@

  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

```{r water masses, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox and 1 outside. Note that several CTD have been replace in situ. The sal_insitu variable combine all these CTD salinity measurements:

- 1 SBE45 inside the Ferrybox (sal_fb)
- 1 CTD at 11 meters depth (sal_insitu)

@@

### **Sal FB / Sal *in situ* **
```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))
  d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(datetime > "2019-12-26 00:00:00", NA, sal),
                 sal_insitu = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu))

fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu , nperm = 99)

p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu, y= sal_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
print(p_sal_fb_sal_insitu)

d_all$diff_sal_fb_insitu <- d_all$sal_insitu - d_all$sal_fb
mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)

# PLOT
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

@@

## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:

- 1 SBE45 inside the Ferrybox (temp_fb)
- 1 seaFET T°C inside the seaFET at 11 meters depth (T_seaF)
- 1 SBE38 at 11 meters depth (temp_insitu)

@@

### **T seaFET / T in situ **
```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
d_all <- d_all %>%
  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))

fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)

pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
print(pTseaf_Tinsi)
